Assessing landscape N removal in coastal New England catchments using the

### 2023-09-29 manuscript/manuscript.Rmd
blank commit
Figure 4 fix. A and B are reversed.

huc <- niantic_data$huc
streams <- st_intersection(huc, niantic_data$streams)
x <- c(pta[1], ptb[1])
y <- c(pta[2], ptb[2])
labels <- c("B", "A")
pts_df <- data.frame(x,y,labels)
ab_plot <- st_as_sf(pts_df, coords = c("x","y"), crs = aea)

>>>>

huc <- niantic_data$huc
streams <- st_intersection(huc, niantic_data$streams)
x <- c(pta[1], ptb[1])
y <- c(pta[2], ptb[2])
labels <- c("A", "B")
pts_df <- data.frame(x,y,labels)
ab_plot <- st_as_sf(pts_df, coords = c("x","y"), crs = aea)
